HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
   \begin{tikzpicture}
     [level 1/.style={sibling distance=7.5em},
       level 2/.style={sibling distance=5em},
       level 3/.style={sibling distance=5em},
       level 4/.style={sibling distance=3em}]
     %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
     %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
   \node (ROOT) [label={B}] [fill=blue, circle] {}
   child {node (H3) [label={A}] [fill=yellow,circle] {}
     child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
     child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
       child {node [label={}] {became} edge from parent node[left]  {}}
       child {node [label={}] {a} edge from parent node[left]  {}}
       child {node [label={}] {passion} edge from parent node[left]  {}}
     }
     child {node (H2) [label={A}] [fill=yellow,circle] {}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
       child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
       child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
       child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
     }
   }
   child {node {} edge from parent[draw=none] {}}
   child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
     child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
   }
   child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
   child {node (H5) [label={A}] [fill=yellow,circle] {}  
     child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
     child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
   };
   \draw[dashed] (H5) -> (she) ;

   \com{
   child {node (H1) [label={\#8}] [fill=black,circle] {}
     child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
       %child {node {to Paris} edge from parent node[right] {$A$}}
       edge from parent node[left] {$H$}
     }
     child {node (H2) [label={\#9}] [fill=black,circle] {}
       child {node  {} edge from parent[draw=none]}
       child {node  {} edge from parent[draw=none]}
       child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
       child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
       child {node [label={\#10}] [fill=black,circle] {}
         child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
         child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
         edge from parent node[right] {$A$}}
       %child {node {to Paris} edge from parent node[right] {$A$}}
       edge from parent node[left] {$H$}
     };
     \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
     }
   \end{tikzpicture}
  \\
  \end{adjustbox}
  \adjustbox{width=\textwidth,center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}

>>>>

\begin{figure*}
  \begin{adjustbox}{trim=2.3cm 0 0 0}
   \begin{tikzpicture}
     [ level distance=12mm,
	   level 1/.style={sibling distance=7.5em,level distance=7mm},
       level 2/.style={sibling distance=5em,level distance=12mm},
       level 3/.style={sibling distance=5em},
       level 4/.style={sibling distance=3em}]
     %[semithick, x=2.4cm,y=0.8cm, >=latex, baseline=7ex,
     %  inner sep=.3ex, outer sep=.7ex, minimum size=1.2ex,->]
   \node (ROOT) [label={B}] [fill=blue, circle] {}
   child {node (H3) [label={A}] [fill=yellow,circle] {}
     child {node [label={[red]:R}] {Golf} edge from parent node[left] {}}
     child {node (H1) [label={[orange]30:O}] [fill=orange,circle] {}
       child {node [label={}] {became} edge from parent node[left]  {}}
       child {node [label={}] {a} edge from parent node[left]  {}}
       child {node [label={}] {passion} edge from parent node[left]  {}}
     }
     child {node (H2) [label={A}] [fill=yellow,circle] {}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node {} edge from parent[draw=none] {}}
       child {node [label={[red]:R}] {for} edge from parent node[left]  {}}
       child {node [label={[green]:G}] {his} edge from parent node[left]  {}}
       child {node [label={[orange]:O}] {oldest} edge from parent node[left]  {}}
       child {node [label={[green]:G}] {daughter} edge from parent node[left]  {}}
     }
   }
   child {node {} edge from parent[draw=none] {}}
   child {node (H4) [label={[]30:A}] [fill=yellow,circle] {}
     child {node (she) [label={[green]:G}] {she} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {attended} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {daily} edge from parent node[left]  {}}
     child {node [label={[green]:G}] {lessons} edge from parent node[left]  {}}
   }
   child {node [label={[red]:R}] {and} edge from parent node[left]  {}}
   child {node (H5) [label={A}] [fill=yellow,circle] {}  
     child {node [label={[red]:R}] {greatly} edge from parent node[left] {}}
     child {node [label={[orange]:O}] {improved} edge from parent node[left] {}}
   };
   \draw[dashed] (H5) -> (she) ;

   \com{
   child {node (H1) [label={\#8}] [fill=black,circle] {}
     child {node [label={\#2}] {graduation} edge from parent node[right] {$P$}}
       %child {node {to Paris} edge from parent node[right] {$A$}}
       edge from parent node[left] {$H$}
     }
     child {node (H2) [label={\#9}] [fill=black,circle] {}
       child {node  {} edge from parent[draw=none]}
       child {node  {} edge from parent[draw=none]}
       child {node [label={\#3}] (Tom) {Tom} edge from parent node[right] {$A$}}
       child {node [label={\#4}] {moved} edge from parent node[right] {$P$}}
       child {node [label={\#10}] [fill=black,circle] {}
         child {node [label={\#5}] {to} edge from parent node[right] {$R$}}
         child {node [label={\#6}] {NYC} edge from parent node[right] {$C$}}
         edge from parent node[right] {$A$}}
       %child {node {to Paris} edge from parent node[right] {$A$}}
       edge from parent node[left] {$H$}
     };
     \draw (H1) -> (Tom) node[midway, right] {$A$ \hspace{0.2cm}};
     }
   \end{tikzpicture}
  \\
  \end{adjustbox}
    % Ondrej removed the width=\textwidth from the options below to keep font
	% unenlarged:
  \adjustbox{center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}
